---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Input formats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE,
  include = TRUE
)
```

### Installing the package

The `lineaGT` R package can be installed directly from GitHub using `devtools`:

```{r install_pkg}
devtools::install_github("caravagnalab/lineaGT")
```

Once installed, load the package in your R session:

```{r load_pkg}
library(lineaGT) 
```

### Installing Python dependencies

The `lineaGT` package relies on the Python module `pylineaGT`. The recommended approach is to install these Python dependencies inside a dedicated conda environment.

This can be done from R using the `reticulate` package through the following steps.

- if Miniconda is not already available on your system, you can install it using through [`reticulate`](https://rstudio.github.io/reticulate/reference/install_miniconda.html):

```{r}
install_miniconda(path=miniconda_path(), update=TRUE, force=FALSE)
```

- create a new conda environment with Python version 3.10:

```{r}
reticulate::conda_create(envname="lineaGT", python_version="3.8")
```

- activate the new conda environment within the current R session:

```{r}
reticulate::use_condaenv("lineaGT")
```

- install the `pylineaGT` Python module using pip inside the conda environment:

```{r}
reticulate::conda_install(envname="lineaGT", packages="pylineaGT", pip=TRUE)
```

## Fitting a `lineaGT` object

Before fitting a `lineaGT` object with the `fit()` or the `fit_growth_rates()` functions, make sure that the correct conda environment is active so that the `pylineaGT` module can be accessed:

```{r}
reticulate::use_condaenv("lineaGT")
```

Functions that rely on `pylineaGT` include an additional argument, `py`, which allows you to explicitly pass the imported Python module. This ensures that the correct version of `pylineaGT` is used.

```{r, eval=FALSE}
reticulate::use_condaenv("lineaGT")
py = reticulate::import("pylineaGT")
x = fit(..., py=py)
# or
x = fit_growth_rates(..., py=py)
```
