---
title: "Lineage inference"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`lineaGT` Bayesian models are implemented in Python using the Pyro probabilistic programming language and thus require a working Python programme and `pylineaGT` package. We recommend reading the [Get Started](https://caravagnalab.github.io/lineaGT/articles/lineaGT.html) article to correctly install the Python package.

```{r, collapse=TRUE}
reticulate::conda_create(envname="lineaGT", python_version="3.8")
reticulate::use_condaenv("lineaGT")
reticulate::conda_install(envname="lineaGT", packages="pylineaGT", pip=TRUE)
py_pkg = reticulate::import("pylineaGT")
```

Remember to load the new environment in order to have the `pylineaGT` module accessible.

```{r setup}
library(lineaGT)
library(magrittr)
reticulate::use_condaenv("lineaGT")
```

The coverage dataset can be filtered calling the `filter_dataset()` function.

```{r loading data}
data(cov.df.example)
data(vaf.df.example)
```

```{r data filtering}
cov.example.filt = cov.df.example %>%
  filter_dataset(min_cov=5, min_frac=0.05)

cov.example.filt
```

# Fitting the model

```{r warning=FALSE, collapse=TRUE}
x = fit(
  cov.df = cov.example.filt,
  vaf.df = vaf.df.example,
  steps = 500,
  k_interval = c(5, 15),
  infer_growth = TRUE,
  timepoints_to_int = unlist(list("t1"=60, "t2"=150))
  )
```

Printing the fitted object information regarding the data:

-   lineages and timpoints present in the data,

-   number of integration sites,

-   number of inferred clones of ISs, estimated via model selection on the input range of number of clusters,

-   for each clone, the number of assigned ISs and the mean coverage, per timepoint and lineage.

```{r}
x
```
