---
title: "Lineage inference"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lineaGT)
library(magrittr)
```

The coverage dataset can be filtered calling the `filter_dataset()` function.

```{r loading data}
data(cov.df.example)
data(vaf.df.example)
```

```{r data filtering}
cov.example.filt = cov.df.example %>%
  filter_dataset(min_cov=5, min_frac=0.05)

cov.example.filt
```

# Fitting the model

```{r warning=FALSE}
x = fit(
  cov.df = cov.example.filt,
  vaf.df = vaf.df.example,
  steps = 500,
  # n_runs = 1,
  k_interval = c(5, 15),
  timepoints_to_int = unlist(list("t1"=60, "t2"=150))
  )
```

Printing the fitted object information regarding the data:

-   lineages and timpoints present in the data,

-   number of integration sites,

-   number of inferred clones of ISs, estimated via model selection on the input range of number of clusters,

-   for each clone, the number of assigned ISs and the mean coverage, per timepoint and lineage.

```{r}
data(x.example)
x.example
```
